Supplemental Materials: Activity Videos

### 2021-09-21 paper/manuscript.Rmd
condensed abstract

abstract: |
  Early parenting practices help shape children’s future outcomes. In particular, high-quality early interactions can facilitate language learning and school performance. Phone-based parenting applications can deliver low-cost interventions on parenting style, yet relatively little is known about the efficacy of this approach. In two studies (N=142; 79 female; ages 6-24 months), we investigated effects of short videos on parent behavior. Parents watched videos depicting age-appropriate parent-child activities from a parenting app. After watching the videos, parents spoke more and made more bids for joint attention. These results suggest that activity videos can lead to local changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
wordcount         : "5509"
bibliography      : ["library.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
header-includes:
  - \usepackage{float}
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

ttr_means <- e1ld %>% group_by(Condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means) # -1.68 - should we report this?
```

@@

```{r, e2-effect-size, echo=F, include=F}
ttr_means <- e2ld %>% group_by(Condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means)
```

>>>>

abstract: |
  Early parenting practices help shape children’s future outcomes. In particular, high-quality early interactions can facilitate language learning and school performance. Phone-based parenting applications can deliver low-cost interventions on parenting style, yet little is known about the efficacy of this approach. In two studies (N=142; 79 female; ages 6-24 months; 74 white, 31 Asian, 31 biracial, 3 black, 12 other; 31 Hispanic), we investigated effects of short videos on parent behavior. After parents watched videos depicting age-appropriate parent-child activities, parents spoke more (d=0.83) and made more bids for joint attention (d=1.03). These results suggest that activity videos can lead to local changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
wordcount         : "5509"
bibliography      : ["library.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
header-includes:
  - \usepackage{float}
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

ttr_means <- e1ld %>% group_by(condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means) # -1.68 - should we report this?
```

@@

```{r, e2-effect-size, echo=F, include=F}
ttr_means <- e2ld %>% group_by(condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means) # -1.28

# overall effect sizes for abstract:
e1e2_tok <- e1ld %>% select(sid, condition, types, tokens, TTR, MTLD) %>%
  bind_rows(e2ld %>% select(sid, condition, types, tokens, TTR, MTLD)) %>% 
  group_by(condition) %>%
  summarise(mean = mean(tokens), sd = sd(tokens))
cohens_d(e1e2_tok) # d=0.83 (E1: 0.94, E2: .77)

e1e2_ja <- e1ja %>% mutate(condition = factor(ifelse(Condition=="No Video", "con", "exp"))) %>%
  select(SID, condition, bids, pja, cja) %>%
  bind_rows(e2ja %>% select(SID, condition, bids, pja, cja)) %>% 
  group_by(condition) %>%
  summarise(mean = mean(bids), sd = sd(bids))
cohens_d(e1e2_ja) # d=1.03
# After watching the videos, parents spoke more (d=0.83) and made more bids for joint attention (d=1.03).
```

### 2021-09-21 paper/supp-ActivityVideos.Rmd
anonymous view-only links for blind peer review
condensed abstract

---
title: "Appendix: Activity Videos"
output: pdf_document
---

@@

@@

@@

@@

>>>>

---
title: 'Supplemental Materials: Activity Videos'
output:
  word_document: default
  pdf_document: default
---
<!-- 522 words -->

@@

(The same as Video C in Exp. 1, but with different props.)

@@

(The same as Video D in Exp. 1.)

@@

(The same as Video E in Exp. 1.)

@@

(The same as Video F in Exp. 1.)
